HTW Full

### 2024-04-05 Sections/htw_full.qmd
toc

---
title: HTW Full
date: last-modified
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
---

>>>>

---
title: HTW Full
date: last-modified
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
repo-actions: false
execute: 
  warning: false
  eval: true
---
